GravExplain

### 2019-12-16 paper/paper_main.tex
added an extra acknowledgement and moved paper tex into own directory

\section{Introduction}
GravExplain

@@

>>>>

\section{Introduction}
A network of gravitational wave observatories around the world are .....

A Michelson interferometer is commonly used by gravitational wave research groups to demonstrate gravitational wave science to non-specialist audiences. 
These are typically table-top demonstrations

@@

The authors are grateful to Deeksha Beniwal, Sebastian Ng, and Craig Ingram for their advice and work in designing the interferometer.
